---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.2.1
  kernelspec:
    display_name: R 3.6.1
    language: R
    name: ir361
---

<!-- #region {"slideshow": {"slide_type": "slide"}} -->
# Data validation
<!-- #endregion -->

<!-- #region {"slideshow": {"slide_type": "subslide"}} -->
## Setup
<!-- #endregion -->

```{r}
library(tidyverse)
```

```{r slideshow={'slide_type': 'subslide'}}
na_summary <- arrow::read_feather("data/na_summary.feather")

head(na_summary)
```

<!-- #region {"slideshow": {"slide_type": "slide"}} -->
## Check for duplicates
<!-- #endregion -->

<!-- #region {"slideshow": {"slide_type": "subslide"}} -->
### Annual report inconsistencies
<!-- #endregion -->

<!-- #region {"slideshow": {"slide_type": "subslide"}} -->
If there are no inconsistent, the number of unique entries should be the same, regardless of whether or not we include only company and year, or include variables of interest, too.
<!-- #endregion -->

```{r}
na_summary %>%
    select(companyid, annualreportdate) %>%
    n_distinct()

na_summary %>%
    select(companyid, annualreportdate, numberdirectors, nationalitymix, genderratio, companyid) %>%
    n_distinct()
```

Looks correct.

```{r slideshow={'slide_type': 'subslide'}}
na_summary %>%
    select(companyid, annualreportdate) %>%
    n_distinct()

na_summary %>%
    select(companyid, annualreportdate, isin) %>%
    n_distinct()
```

There are 9,040 inconsistencies with the ISIN code.

<!-- #region {"slideshow": {"slide_type": "subslide"}} -->
### Multiple annual reports in a year
<!-- #endregion -->

If there are multple annual reports in any year, the number of entries should be reduced when we extract only the year from the annual report date column.

```{r}
na_summary %>%
    select(companyid, annualreportdate) %>%
    n_distinct()
```

```{r}
na_summary %>%
    mutate(year = lubridate::year(annualreportdate)) %>%
    select(companyid, year) %>%
    n_distinct()
```

There are 632 instances of two reports being filled in one year.
